---
title: "R Notebook"
output: html_notebook
---

This is to explain and keep track of the project. The overall aim of this entropy
work is to create:

1) A segregation index for MSAs in the US
2) Use spatial models to get margin of error / credible intervals for the indices

# Data
We use data on the number of people living in a particular income group in a 
census tract from Rory. Using that data we have enough to create point estimates
for the segregation index. However to create credible intervals we need spatial
polygon files to work out contiguity matrices for the spatial model.

First we have to load in the locations of WHERE we have stored all the data on
1) population from Rory and 2) the census tract spatial data.

```{r}
source('Source (laptop version).R')
```

Other functions to use later include the entropy function which takes in a 
dataframe or table with named cols. It creates the entropy index of interest from
the data.

```{r}
source('Entropy function.R')
```

##  Joining census tract population to census shp files

To start doing this we have to have the shapefiles from the US census which is
simply split off into several individual files for states. So we have written 
code to batch download it.

```{r}
# Do not run (unless these files are needed)
#source('Downloading shp files from US.R')
```

For the actual join, we process the data and merge it. 















